Future CMB delensing with galaxies surveys.

### 2017-03-17 Notes/DES_rec_phi_paper.tex
tex
tex fix

\documentclass[onecolumn,amsmath,amssymb,floatfix,superscriptaddress,notitlepage,aps,prd]{revtex4-1}
\usepackage{bm}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{graphicx,epsfig}
\usepackage{hyperref}
\usepackage{ifthen}
\usepackage{xstring}
\usepackage{graphicx}\usepackage[top=2.5 cm, bottom=2.5 cm, left=1.05in, right=1.05in]{geometry}
\usepackage[applemac]{inputenc}
\usepackage{amsmath,amssymb} 
\usepackage{color}
\usepackage{epstopdf}
\usepackage[caption=false]{subcaption}
\epstopdfDeclareGraphicsRule{.gif}{png}{.png}{convert gif:#1 png:\OutputFile}
\AppendGraphicsExtensions{.gif}
% notes to make comment

\newcommand{\note}[1]{\textsc{#1}}

% For various journals
%\newcommand{\apj}{ApJ}
\newcommand{\physrep}{Physics Reports}
\newcommand{\jcap}{JCAP}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\aap}{A\&A}
\newcommand{\mnras}{MNRAS}
%\newcommand{\prd}{Phys. Rev. D}
\newcommand{\physrev}{Phys. Rev.}
\newcommand{\physrevlett}{Phys. Rev. Lett.}

%--------- NEW COMMAND STUFF

\def\simlt{\lesssim}
\def\simgt{\gtrsim}
\newcommand{\Omegamzero}{\Omega_{{\rm m,0}}}
\newcommand{\alm}{a_{lm}}

%\newcommand{\l}{\ell}}

@@

\newcommand{\refsec}[1]{section~\ref{sec:#1}}
\newcommand{\reftab}[1]{Tab.~\ref{tab:#1}}
\newcommand{\refeq}[1]{Eq.~(\ref{eqn:#1})}
\newcommand{\refssec}[1]{section~\ref{subsec:#1}}
\newcommand{\reffig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\refFig}[1]{Fig.~\ref{fig:#1}}

@@

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{natbib}
\newcommand{\bx}{{\bf x}}
\newcommand{\bk}{{\bf k}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bP}{{\bf\Psi}}
\newcommand{\bs}{{\bf s}}
\newcommand{\cs}{{\cal S}}
\newcommand{\by}{{\bf y}}
\newcommand{\deltar}{\delta_{\rm recon}}%\def\lcdm{$\Lambda$CDM}
\def\arcsec{$^{\prime\prime}$}
\def\nl{N_\ell}
\def\sl{S_\ell}
\def\ublu{\bl'}
\newcommand{\conv}[2]{\left(\frac{#1}{#2}\right)}
\def\arctanh{\mathop{\rm arctanh}\nolimits}
%\renewcommand{\eqref}[1] {equation $($\ref{#1}$)$}
\newcommand{\comment}[1]{{}}
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\beqn{\begin{eqnarray}}
\def\eeqn{\end{eqnarray}}
\def\a{\alpha}
\def\cl{C_{l}}
\def\h{\mathrm{h}}
\def\d{\rmn{d}}
\def\pa{\partial}
\def\deldel#1#2{\frac{\pa{#1}}{\pa{#2}}}
\def\ba{\bm{\alpha}}
\def\fracj#1#2{{\textstyle{#1\over#2}}}
\def\bxi{\bm{\xi}}
\def\half{\frac{1}{2}}
\def\ti{\widetilde}
\def\O{\Omega}
\def\OL{\Omega_\Lambda}
\def\Om{\ensuremath{\Omega_{\mathrm{m}}}}
\def\Ob{\ensuremath{\Omega_{\mathrm{b}}}}
\def\Oc{\ensuremath{\Omega_{\mathrm{CDM}}}}
\def\msol{\ensuremath{M_\odot}}
\def\l{\left}
\def\r{\right}
\def\o{\omega}
\def\gcm{\textrm{g cm$^{-3}$}}
\def\2gcm{\textrm{g cm$^{-2}$}}
\def\Scr{\Sigma_{\mathrm{crit}}}
\def\rcr{\rho_{\mathrm{crit}}}
\def\phidot{\ensuremath{\dot\phi_{\bl,\bl'}}}
\def\ddelta{\ensuremath{\dot\delta}}
\def\modu#1{\l |{#1}\r |}
\def\av#1{\l \langle{#1}\r \rangle}
\def\hmpc{\:{h}^{-1}\mathrm{Mpc}}
\def\th{\Theta}
\def\tth{\tilde\Theta}
\def\sg{\sigma}
\def\Sig{\Sigma}
\def\cf{{\cal F}}
\def\k{\kappa}
\def\P{{P}}
\def\pnl{{P}_{{\!\textrm{\tiny NL}}}}
\def\dnl{\Delta_{\text{\scriptsize NL}}}
\def\kmin{\k_{\mathrm{min}}}
\def\kmax{\k_{\mathrm{max}}}
\def\hires{the \emph{highRes} experiment}
\def\lores{the \emph{lowRes} experiment}
\def\ktot{\k_{\mathrm{tot}}}
\def\hunit{\ensuremath{\mathrm{km}{\mathrm{s}^{-1}} \mathrm{Mpc}^{-1}}}
\def\H0{\ensuremath{\mathrm{H}_0}}
\def\nn{\nonumber}
\def\lin{\mathrm{lin}}
\def\ISW{\mathrm{ISW}}
\def\bl{\bmm{l}}
\def\bL{\bmm{L}}
\def\fsky{f_{\mathrm{sky}}}
\newcommand{\E}[1]{\times 10^{#1}}
\newcommand{\bmm}[1]{{\mathbf{#1}}}
\newcommand{\new}[1]{{\color{blue} #1}}
\newcommand{\bsection}[1]{\section{\uppercase{#1}}}

@@

@@

%=======================================
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.]{../images/spectra.pdf}
\caption{Correlation factor between galaxies survey and CMB lensing potential as a function of the multipole $\ell$. The ``CIB+D.E.S'' factor has been computed using \refeq{rho-combined}}
\end{center}
\label{fig:corr}

@@

\section{Data}
\label{sec:data}

D.E.S, Planck CIB, DESI?
\cite{hall:2010,sherwin:2015,ade:2014,hanson:2013,szapudi:2001,0004-637X-567-1-2,planck-collaboration:2014,planck-collaboration:2014a,planck-collaboration:2011,plank-collaboration:2014,boulanger:1996,lewis:2006}

@@

\subsection{Bias uncertainties degradation}
\bibliographystyle{plain}
\bibliography{DES_rec_phi_paper}

>>>>

\documentclass[onecolumn,amsmath,amssymb,floatfix,superscriptaddress,notitlepage,aps,prd]{revtex4-1}
\usepackage{bm}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{graphicx,epsfig}
\usepackage{hyperref}
\usepackage{ifthen}
\usepackage{xstring}
\usepackage{graphicx}\usepackage[top=2.5 cm, bottom=2.5 cm, left=1.05in, right=1.05in]{geometry}
\usepackage[applemac]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{color}
\usepackage{epstopdf}
\usepackage[caption=false]{subcaption}
\epstopdfDeclareGraphicsRule{.gif}{png}{.png}{convert gif:#1 png:\OutputFile}
\AppendGraphicsExtensions{.gif}
% notes to make comment
\newcommand{\al}[1]{\begin{align} #1 \end{align}}

\newcommand{\note}[1]{\textsc{#1}}
	\newcommand{\bR}[1]{{\bm {\mR{#1}}} }

\def\l{\ell}
% For various journals
%\newcommand{\apj}{ApJ}
\newcommand{\physrep}{Physics Reports}
\newcommand{\jcap}{JCAP}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\aap}{A\&A}
\newcommand{\mnras}{MNRAS}
%\newcommand{\prd}{Phys. Rev. D}
\newcommand{\physrev}{Phys. Rev.}
\newcommand{\physrevlett}{Phys. Rev. Lett.}

\newcommand{\nver}{\hat{\mathbf{n}}}
\newcommand{\cov}{\text{Cov}}
\newcommand{\Nsim}{N_{\text{sim}}}
\newcommand{\new}[1]{{\textcolor{blue}{\bf #1}}}
%--------- NEW COMMAND STUFF
	\newcommand{\PD}[2]{\dfrac{\partial #1}{\partial #2}}

\def\simlt{\lesssim}
\def\simgt{\gtrsim}
\newcommand{\Omegamzero}{\Omega_{{\rm m,0}}}
\newcommand{\alm}{a_{lm}}
	% * subscript
	\def\rom#1{%
		_{\mathrm{#1}}%
	}%
%\newcommand{\l}{\ell}}

@@

\newcommand{\refsec}[1]{section~\ref{sec:#1}}
\newcommand{\reftab}[1]{Tab.~\ref{tab:#1}}
\newcommand{\refeq}[1]{Eq.~(\ref{eqn:#1})}
\newcommand{\refssec}[1]{section~\ref{subsec:#1}}
\newcommand{\reffig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\refFig}[1]{Fig.~\ref{fig:#1}}
	\newcommand{\mR}[1]{\mathrm{#1}}   % mathrm

@@

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{natbib}
\newcommand{\bx}{{\bf x}}
\newcommand{\bk}{{\bf k}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bP}{{\bf\Psi}}
\newcommand{\bs}{{\bf s}}
\newcommand{\cs}{{\cal S}}
\newcommand{\by}{{\bf y}}
\newcommand{\deltar}{\delta_{\rm recon}}%\def\lcdm{$\Lambda$CDM}
\def\arcsec{$^{\prime\prime}$}
\def\nl{N_\ell}
\def\sl{S_\ell}
\def\ublu{\bl'}
\newcommand{\conv}[2]{\left(\frac{#1}{#2}\right)}
\def\arctanh{\mathop{\rm arctanh}\nolimits}
%\renewcommand{\eqref}[1] {equation $($\ref{#1}$)$}
\newcommand{\comment}[1]{{}}
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\beqn{\begin{eqnarray}}
\def\eeqn{\end{eqnarray}}
\def\a{\alpha}
\def\cl{C_{l}}
\def\h{\mathrm{h}}
\def\d{\rmn{d}}
\def\pa{\partial}
\def\deldel#1#2{\frac{\pa{#1}}{\pa{#2}}}
\def\ba{\bm{\alpha}}
\def\fracj#1#2{{\textstyle{#1\over#2}}}
\def\bxi{\bm{\xi}}
\def\half{\frac{1}{2}}
\def\ti{\widetilde}
\def\O{\Omega}
\def\OL{\Omega_\Lambda}
\def\Om{\ensuremath{\Omega_{\mathrm{m}}}}
\def\Ob{\ensuremath{\Omega_{\mathrm{b}}}}
\def\Oc{\ensuremath{\Omega_{\mathrm{CDM}}}}
\def\msol{\ensuremath{M_\odot}}
\def\l{\left}
\def\r{\right}
\def\o{\omega}
\def\gcm{\textrm{g cm$^{-3}$}}
\def\2gcm{\textrm{g cm$^{-2}$}}
\def\Scr{\Sigma_{\mathrm{crit}}}
\def\rcr{\rho_{\mathrm{crit}}}
\def\phidot{\ensuremath{\dot\phi_{\bl,\bl'}}}
\def\ddelta{\ensuremath{\dot\delta}}
\def\modu#1{\l |{#1}\r |}
\def\av#1{\l \langle{#1}\r \rangle}
\def\hmpc{\:{h}^{-1}\mathrm{Mpc}}
\def\th{\Theta}
\def\tth{\tilde\Theta}
\def\sg{\sigma}
\def\Sig{\Sigma}
\def\cf{{\cal F}}
\def\k{\kappa}
\def\P{{P}}
\def\pnl{{P}_{{\!\textrm{\tiny NL}}}}
\def\dnl{\Delta_{\text{\scriptsize NL}}}
\def\kmin{\k_{\mathrm{min}}}
\def\kmax{\k_{\mathrm{max}}}
\def\hires{the \emph{highRes} experiment}
\def\lores{the \emph{lowRes} experiment}
\def\ktot{\k_{\mathrm{tot}}}
\def\hunit{\ensuremath{\mathrm{km}{\mathrm{s}^{-1}} \mathrm{Mpc}^{-1}}}
\def\H0{\ensuremath{\mathrm{H}_0}}
\def\nn{\nonumber}
\def\lin{\mathrm{lin}}
\def\ISW{\mathrm{ISW}}
\def\bl{\bmm{l}}
\def\bL{\bmm{L}}
\def\fsky{f_{\mathrm{sky}}}
\newcommand{\E}[1]{\times 10^{#1}}
\newcommand{\bmm}[1]{{\mathbf{#1}}}
\newcommand{\bsection}[1]{\section{\uppercase{#1}}}

@@

\section{Introduction}

@@

%=======================================
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{../images/spectra.pdf}
\caption{Correlation factor between galaxies survey and CMB lensing potential as a function of the multipole $\ell$. The ``CIB+D.E.S'' factor has been computed using \refeq{rho-combined}}
\end{center}
\label{fig:corr}

@@

\section{Tracers Model}
\label{sec:data}

In this equation, $\chi(z)$ is the comoving distance to redshift $z$, $\chi_*$ is the comoving distance to the last-scattering surface at $z_*\simeq 1090$, $H(z)$ is the Hubble factor at redshift $z$, $c$ is the speed of light, and $\Psi(\chi(z)\nver,z)$ is the three-dimensional gravitational potential at a point on the photon path given by $\chi(z)\nver$. Note that the deflection angle is given by $\mathbf{d}(\nver) = \nabla\phi(\nver)$, where $\nabla$ is the the two-dimensional gradient on the sphere. Because the lensing potential is an integrated measure of the projected gravitational potential, taking the two-dimensional Laplacian of the lensing potential we can define the lensing convergence $\kappa(\nver) = -\case{1}{2}\nabla^2\phi(\nver)$, which depends on the projected matter overdensity $\delta$ \citep{bart01}:
\begin{equation}
\kappa(\nver) = \int_0^{z_*} dz\, W^{\kappa}(z)\delta(\chi(z)\nver,z).
\label{eqn:wkappa}
\end{equation}
The lensing kernel $W^{\kappa}$ is
%
\begin{equation}
W^{\kappa}(z) = \frac{3\Omega_{\rm m}}{2c}\frac{H_0^2}{H(z)}(1+z)\chi(z)\frac{\chi_*-\chi(z)}{\chi_*},
\end{equation}
%
where $\Omega_{\rm m}$ and $H_0$ are the present-day values of the Hubble and matter density parameters, respectively.

%----------------------------------------------------------------------------------------------------%
%\begin{eqnarray} \label{PS}
%	C_\l^{XY} = \frac{2}{\pi}\Int{}{k}{k^2} P_{init}(k) \Delta_\l^X(k)\Delta_\l^Y(k) 
%	\,, 
%\end{eqnarray}
%----------------------------------------------------------------------------------------------------%
where $P_{init}(k)$ is the scalar power spectrum at an early time with $k$ being the Fourier wave 
number. The functions $\Delta^X\l(k)$ and $\Delta^Y\l(k)$ are one of the following (see e.g., 
\cite{Hu:2000ee,LoVerde:2006cj}):
%----------------------------------------------------------------------------------------------------%
%\begin{eqnarray}
%
%	\Delta^I_\l(k) &= k^2 \INT{}{z}{}{0}{z_{\rm max}} b(z) \D{N}{z}(z) D(z) j_\l(k\chi(z)) 
%	\,, \label{eq:Delta^I} \\
%	\Delta^\grad_\l(k) &= \frac{3\Omega\rom{m}H_0^2}{2}
%	\notag \\
%		&\times \INT{}{\chi}{}{0}{\chi_*} 
%			\frac{\chi_*-\chi}{\chi_*\chi}\,\frac{D(z(\chi))}{a(\chi)}\,j_\l(k\chi)
%	\,. 
%	
%\end{eqnarray}

%----------------------------------------------------------------------------------------------------%

\subsection{Galaxies}

The galaxy overdensity $g(\nver)$ in a given direction on the sky is also expressed as a LOS integral of the matter overdensity:
\begin{equation}
g(\nver) = \int_0^{z_*} dz\, W^{g}(z)\delta(\chi(z)\nver,z),
\end{equation}
where the kernel is
\begin{equation}
\label{eqn:wg}
\begin{split}
W^{g}(z) &= \frac{b(z)\frac{dN}{dz}}{\Bigl(\int dz'\,\frac{dN}{dz'}\Bigr)} + \frac{3\Omega_{\rm m}}{2c}\frac{H_0^2}{H(z)}(1+z)\chi(z) \\
&\times \int_z^{z_*}dz'\,\Bigl(1-\frac{\chi(z)}{\chi(z')}\Bigr)(\alpha(z')-1)\frac{dN}{dz'}.
\end{split}
\end{equation}

\subsection{Cosmic infrared Background}
\label{sec:cib}
In this work, the CMB lensing potential is estimated from maps of the cosmic infrared background (CIB).

Following \cite{Addison:2011se}, we model the CIB power as $C_{\ell}^{{\rm CIB}\mbox{-}{\rm CIB}} = 3500 (l/3000)^{-1.25} {\rm Jy^2 / sr}$.
We test that this model provides an accurate fit for the power of the \textit{Herschel} $500\,\mu$ map used in this work.
For the cross-spectrum $C_{\ell}^{{\rm CIB}\mbox{-}\phi}$, we use the single-SED model of~\cite{hall10}.
This places the peak of the CIB emissivity at redshift $z_c = 2$ with a broad redshift kernel of width $\sigma_z = 2$.
This model is rescaled to agree with the results of
~\citet{Holder:2013hqu} and \citet{planck2013XVIII} by choosing the corresponding linear bias parameter.
Other multi-frequency CIB models are available \citep[e.g.,][]{Bethermin:2013nza}; however, given the level of noise, we are relatively insensitive to this choice.
With these assumptions, depending on angular scale, $45-65\%$ of the CIB is correlated with the CMB lensing potential, as shown in \reffig{CIB}.

\subsection{Weak Lensing}
\cite{hall:2010,sherwin:2015,ade:2014,hanson:2013,szapudi:2001,0004-637X-567-1-2,planck-collaboration:2014,planck-collaboration:2014a,planck-collaboration:2011,plank-collaboration:2014,boulanger:1996,lewis:2006}
\subsection{Internal CMB lensing}

@@

%----------------------------------------------------------------------------------------------------%
%\al{
%	F_{ij} &\equiv \sum_{\l=\l\rom{min}}^{100} \frac{2\l+1}{2[C_\l^{\rm BB,res}+N_\l^{\rm BB}]^2}
%		\PD{C^{\rm BB,res}_\l}{\theta_i}\PD{C^{\rm BB,res}_\l}{\theta_j}
%	\notag \\
%	&+ \sum_{L=2}^{1000} \frac{2L+1}{2} 
%		\Tr \left[\bR{C}^{-1}_L\PD{\bR{C}_L}{\theta_i}\bR{C}^{-1}_L\PD{\bR{C}_L}{\theta_j}\right]
%	\,, 
%}
%----------------------------------------------------------------------------------------------------%
where $\theta_i=r$, $b_i$ or $p_i$ \footnote{In our analysis, since the fiducial value of $r$ is zero, 
the derivative of $C_\l^{\rm BB,res}$ is non-zero if $\theta_i=r$.}. 
The covariance matrix of the mass tracers $\bR{C}_L$ is given in Eq.~\eqref{Eq:cov}. 
We compute the derivatives of the power spectra as described in appendix \ref{sec:deriv}. 
Note that we omit the correction of the partial sky coverage since it does not affect our results, i.e.,

\section{Conclusions}

\bibliographystyle{plain}
\bibliography{DES_rec_phi_paper}
